Summary Outcome Tables

### 2020-07-16 summary_tables_outcomes.Rmd
Add flextable for multi-line headers

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(DT)
library(ggplot2)
library(tidyr)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, message = F, warning = F, results='asis')

@@

    index <- index + 1
    cat('####', cm, '\n')
    print(kable(format(temp1, scientific = F), caption = paste('Who Hit Whom (WHW) for ', scen_names[i], 'scenario and ', cas_mode[j], ' mode')))

>>>>

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(flextable)
library(ggplot2)
library(tidyr)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, message = F, warning = F, results='asis')

@@

    index <- index + 1
    cat('\n')
    cat('####', cm, '\n')
    #print(kable(format(temp1, scientific = F), caption = paste('Who Hit Whom (WHW) for ', scen_names[i], 'scenario and ', cas_mode[j], ' mode')))

    ft <- flextable(temp1)
    ft <- add_header_row(ft, values = c(' ', 'strike mode'), colwidths = c(3, ncol(temp1) - 3))
    ft <- merge_v(ft, j = 1:3, part = 'body')

    cat(knit_print(ft))
